\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-12 article.tex
Add comment about bug

\noindent If one were to note the \(\mathit{in}[s]\) and \(\mathit{out}[s]\) sets for each instruction \(s\) for each iteration, one would arrive at the two tables seen in Table \ref{tab:countll-rev-steps} and \ref{tab:countll-steps}.
The number of iterations is nearly halfed when reverseing the list of instructions prior to dataflow as can be seen on \ref{tab:countll-rev-steps} when compared to \ref{tab:countll-steps}.

@@

>>>>

\noindent If one were to note the \(\mathit{in}[s]\) and \(\mathit{out}[s]\) sets for each instruction \(s\) for each iteration, one would arrive at the two tables seen in Table \ref{tab:countll-rev-steps} and \ref{tab:countll-steps}.
The number of iterations is nearly halfed when reverseing the list of instructions prior to dataflow as can be seen on the amount of recursions of Table \ref{tab:countll-rev-steps} when compared to Table \ref{tab:countll-steps}.

@@

\subsection{Test Suite}

In addition to my own cases and other programs from the internet, some cases from the LLVM test suite are also used.

The structure of the test suite repository has a directory of so-called 'single source' C programs totalling to 2113. Of these only 1222 compiled successfully with \texttt{clang -S -emit-llvm} and of these only 624 parsed sucessfuly with the strip utility, of which 425 compiled successfully.

% find ./SingleSource -name '*.c' -exec clang --target=x86_64-unknown-darwin -S -emit-llvm {} \;
